# Week 2 Project

## Tejas Singh!

<!-- leave this material as is -->
Compiled on `r date()`.

```{r include = FALSE}
library(DataComputing)
```
<!-- put your content after this line -->

I got this data from the the Library book use assignment web page (https://dtkaplan.github.io/comp110/Projects/251-Library-Books-github.html)

The data set was downloaded using the following link:
("http://tiny.cc/dcf/Library-small.rda",dest="Library-small.rda")

Downloading the Data
```{r include = FALSE}
download.file("http://tiny.cc/dcf/Library-small.rda",dest="Library-small.rda")
```

**Basics**

Loading the Data
```{r}
load("Library-small.rda")
```

**The Inv Table**

Number of cases:
```{r}
nrow(Inv)
```

Number of variables:
```{r}
ncol(Inv)
```

Names of variables:

```{r}
names(Inv)
```

The codebook:
```{r}
help(Inv)
```

Summary of Table:
```{r}
summary(Inv)
```

In this Table (Inv) each case in the Macalester student libraryis a book with information about a its location, author, pages etc.

Number of books in Table Inv: 
```{r}
Inv %>%group_by(Current.Status) %>%tally()
```

Number of times, books have been checked out in Table (Inv):
```{r}
Inv %>%group_by(Issued.Count) %>%tally()
```
The results show how many times each book has been issued. 


